---
title: "Vignette"
author: "Pietro Zoffoli"
date: "2024-05-16"
output: html_document
---

# My first rmarkdown file

This file contains functions for R scripting in Geo_Ecological Remote Sensing. 

We are going to make use of the following packages:

```{r}
library(imageRy)
library(terra)
library(viridis)
```

In order to visualize the list of data use:

```{r, eval=TRUE}
im.list()
```

in order to imput data you can use the following funcyion:
```{r, eval=TRUE}
mato<-im.import("matogrosso_l5_1992219_lrg.jpg")
```

We are using the set from Mato Grosso and we plot it in RGB space, as:

```{r, eval=TRUE}
im.plotRGB(mato, 1, 2, 3)
```

This plot is related to the following bands: band 1 = NIR, band 2 = red, band 3 = green

We can change the visualization by changing the order of bands in RGB space. 

```{r, eval=TRUE}
im.plotRGB(mato, 2, 1, 3)
```

In order to look at different band combination alltogether we can use :

```{r, eval=TRUE}
par(mfrow=c(1,3))
im.plotRGB(mato, 1, 2, 3)
im.plotRGB(mato, 2, 1, 3)
im.plotRGB(mato, 3, 2, 1)
```

## Calculating spectral indeces:
```{r, eval=TRUE}
dvi<- mato[1]-mato[2]
plot(dvi, col=viridis(100))
```

## Claculating spatial variability
```{r, eval=TRUE}
sd5<-focal(mato[[1]], matrix(1/25, 5, 5), fun=sd)
plot(sd5, col=magma(100))
```













